### 2018-02-05 master/paper.tex
Fix abstract

High productivity of embedded network software is required to run embedded systems within the Internet of Things (IoT).
To improve the productivity, the mruby on TOPPERS embedded component system (TECS) framework, which employs a scripting language (i.e., lightweight Ruby) and supports component-based development, has been proposed.
This paper proposes an extended mruby on TECS framework to use for software development of IoT devices such as sensors and actuators.
The proposed framework enables that mruby programs call TINET, a TCP/IP protocol stack for use in embedded systems, functions.
In addition, this paper proposes two component-based functionalities: a componentized TINET called TINET+TECS and a componentized Two-Level Segregate Fit (TLSF) dynamic memory allocator called TLSF+TECS.
TINET+TECS improves scalability and configurability, and offers software developers high productivity through variable network buffer sizes and the ability to add or remove TCP (or UDP) functionalities.
TINET+TECS utilizes a dynamic TECS component connection method to satisfy the original TINET specifications.
TLSF+TECS is a thread-safe memory allocator that runs at high speed and efficiently consumes memory.
Experimental results of comparison between TINET+TECS and original TINET show that the execution time and memory consumption overhead are reduced and the configurability is improved.
Moreover, the TLSF+TECS functionality which obtains statistical information of mruby VM's memory usage helps developers debug and verify the systems.

>>>>

High productivity of embedded network software is required to run embedded systems within the Internet of Things (IoT).
To improve the productivity, the mruby on TOPPERS embedded component system (TECS) framework, which employs a scripting language (i.e., lightweight Ruby) and supports component-based development, has been proposed.
This paper proposes an extended mruby on TECS framework to use for software development of IoT devices such as sensors and actuators.
The proposed framework enables that mruby programs call TINET, a TCP/IP protocol stack for use in embedded systems, functions.
In addition, this paper proposes two component-based functionalities: a componentized TINET called TINET+TECS and a componentized Two-Level Segregate Fit (TLSF) dynamic memory allocator called TLSF+TECS.
TINET+TECS improves scalability and configurability, and offers software developers high productivity through variable network buffer sizes and the ability to add or remove TCP (or UDP) functionalities.
TINET+TECS utilizes a dynamic TECS component connection method to satisfy the original TINET specifications.
TLSF+TECS is a thread-safe memory allocator that runs at high speed and efficiently consumes memory.
Experimental results of comparison between TINET+TECS and original TINET show that the execution time and memory consumption overhead are reduced and the configurability is improved.
Moreover, the TLSF+TECS functionality which obtains statistical information of mruby VM's memory usage and frequency helps developers debug and verify the systems.
